---
title: "Social Network Analysis with igraph"
author: "Jae In Lee"
date: "2023-03-31"
output: html_document
---

```{r setup}
#install.packages("GGally")
#install.packages("network")
#install.packages("sna")
#install.packages("intergraph")
library(intergraph)
library(GGally)
library(network)
library(sna)
library(readr)
library(ggplot2)
library(igraph)
```

## Data Setup
Go ahead and setup the data for this assignment. In order to do social network analysis for a friend group, we will randomly create variables by randomly choosing two letter from the array of alphabets "A", "B", "C", "D", "E". Then we will create another dataset that collects the unique variable from the dataset and distinguish their gender randomly.


```{r data setup}
# Create sample data
data <- data.frame(matrix(ncol = 2, nrow = 200))
names(data) <- c("first", "second")
for(x in 1:200) {
  a <- c("A", "B", "C", "D", "E")
  bc <- paste(sample(a,1, replace = T), sample(a,1, replace = T), sep = "")
  de <- paste(sample(a,1, replace = T), sample(a,1, replace = T), sep = "")
  ifelse(bc == de, data[x,1] <- paste(sample(a,1, replace = T), sample(a,1, replace = T), sep = ""), data[x,1] <- bc)
  data[x,2] <- paste(de, sep = "")
}

friend <- data.frame(unique(data$first))
for(x in 1:nrow(friend)) {
  g <- c("Female", "Male")
  friend[x,2] <- sample(g,1, replace = T)
}

names(friend) <- c("name", "gender")

```

## Creating Network
Now we use graph_from_data_frame() function to create our network. We can plot the network by using the plot function. 
Afterwards, we will see the vertices of a graph by using the V() function then the E() function to see the edges.
Then we will alter the names and degrees of the vertices of the network.

```{r create network}
# Create Network
net <- graph_from_data_frame(d = data, vertices = friend, directed = T)
plot(net, vertex.size = 2, edge.arrow.size = 0.1, vertex.label.cex = 0.8)
V(net)
E(net)
V(net)$label <- V(net)$name
V(net)$degree <- degree(net)
```


## Histogram of node degree
Create a histogram using the degree of the vertices.

```{r histogram}
hist(V(net)$degree, 
     col = "tomato2", 
     main = "Histogram of Node Degree",
     ylab = "Frequency",
     xlab = "Degree of Vertices")
```


## Color and Plot

Change the colors of the nodes regarding the gender. Do the following.

```{r pressure}
# Color 
V(net)$color <- ifelse(V(net)$gender == "Male", "lightblue", "pink")

# Network diagram
set.seed(222)
plot(net, 
     vertex.size = V(net)$degree,
     edge.arrow.size = 0.1,
     vertex.label.cex = 0.8)
legend("topright", c("Male","Female"), pch=21,
       col="#777777", pt.bg=c("lightblue","pink"), pt.cex=2, cex=.8)
title(main = "Friend Group")
```

## Hub and authorities
Plot the hub (outgoing interactions) and authorities (ingoing interactions) side by side to see which person has the most in or out going connections.

```{r}
hs <- hub_score(net)$vector
as <- authority.score(net)$vector
par(mfrow = c(1,2))
set.seed(123)
plot(net, vertex.size = hs*30,
     main = "Hubs", vertex.color = rainbow(52), edge.arrow.size = 0.1, layout = layout.kamada.kawai)
set.seed(123)
plot(net, vertex.size = as*30,
     main = "Authorities", vertex.color = rainbow(52), edge.arrow.size = 0.1, layout = layout.kamada.kawai)
```

Compile and Finish.

Note that the `echo = FALSE` parameter can be added to the code chunk to prevent printing of the R code that generated the plot.
